### 2015-01-14 fundamentals/examples.tex
simpler words

The functionality of the \Cyclus simulator is illustrated by demonstrations
of its fundamental simulation capabilities and the feasibility the
 community-driven \Cyclus development model.
The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-driven development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fuel cycle simulation capabilities.

>>>>

The functionality and feasibility of the \Cyclus simulator is illustrated by demonstrations
of its fundamental simulation capabilities and growth via its
 community-driven \Cyclus development model.
The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-driven development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fuel cycle simulation capabilities.
